A Meta-analysis of Longevity Estimates of Mosquito Vectors of Disease: Additional Methods

### 2020-01-29 writeUp/supplementary_materials_methods.tex
updated ms with latest results

generated quantities{
  real lifespan[K];
  real survival[K];
  real theta_average[K];
  for(i in 1:K){
    real gon = normal_rng(3.65, 0.4);
    theta_average[i] = beta_rng(phi[i] * kappa[i],
										       (1 - phi[i]) * kappa[i]);
    survival[i] = theta_average[i] ^ (1.0 / gon);
    lifespan[i] = 1.0 / (1.0 - survival[i]); 
  }
}
\end{minted}

>>>>

generated quantities{
  real lifespan[K];
  real survival[K];
  real theta_average[K];
  for(i in 1:K){
    real gon = normal_rng(3.65, 0.4);
    theta_average[i] = beta_rng(phi[i] * kappa[i],
										       (1 - phi[i]) * kappa[i]);
    survival[i] = theta_average[i] ^ (1.0 / gon);
    lifespan[i] = survival[i] / (1.0 - survival[i]); 
  }
}
\end{minted}
